Data Dashboard

### 2020-07-22 analysis/05_market_simulator.Rmd
Got the main renderPlotly to display data

# # Beta's we want for the plotly
# public_political_social_charity_demo <- readRDS(here('analysis', 'output', 'posterior_draws', 'public_political_social_charity_demo.rds')) %>% 
#   group_by(i) %>% 
#   summarize(theta_mean = mean(Theta))
# 
# # RenderPlotly code for testing
# 
# renderPlotly({
#   choice <- df()
#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
#   
#   data <- c(ai_exp_util, gp_exp_util)
#   df <- as.data.frame(matrix(data, 8, 1))
#   
#   df[,2] <- c("Amnesty International", "Green Peace")
#   df[,3] <- c(rep("Utility", 4), rep("Market Share", 4))
#   colnames(df) <- c("Value", "Organization", "Type")
#   
# 
#   
#   ggplotly(ggplot(df, aes(y = Value, x = Organization, fill = Type)) +
#            geom_col() +
#            labs(x="") + 
#            scale_fill_manual(values = c("Amnesty International" = "#FFC30B", "Greenpeace" = "#3fad48")) +
#            theme(legend.position = "none") +
#            facet_wrap(~Type)
#   )
# })

  # ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
  # rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
  # 
  # ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
  # gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
  # ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
  # rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
  # 
  # data <- c(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util, ai_rate, gp_rate, ox_rate, rc_rate)
  # df <- as.data.frame(matrix(data, 8, 1))
  # 
  # df[,2] <- c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")
  # df[,3] <- c(rep("Utility", 4), rep("Market Share", 4))
  # colnames(df) <- c('Value', 'Organization', "Type")

@@

  ggplotly(ggplot(df, aes(y = Value, x = Organization, fill = Type)) +
             geom_col() +
             labs(x="") + 
             scale_fill_manual(values = c("Amnesty International" = "#FFC30B", "Greenpeace" = "#3fad48", "Oxfam" = "#006633", "Red Cross" = "#660000"))+
             theme(legend.position = "none") +
             facet_wrap(~Type)
    )
})
```

>>>>

# # Beta's we want for the plotly
# public_political_social_charity_demo <- readRDS(here('analysis', 'output', 'posterior_draws', 'public_political_social_charity_demo.rds')) %>% 
#   group_by(i) %>% 
#   summarize(theta_mean = mean(Theta))
# 
# # RenderPlotly code for testing
# 
# renderPlotly({
#   choice <- df()
  # ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
  # gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
  # 
  # data <- c(ai_exp_util, gp_exp_util)
  # df <- as.data.frame(matrix(data, 8, 1))
  # 
  # df[,2] <- c("Amnesty International", "Green Peace")
  # df[,3] <- c(rep("Utility", 4), rep("Market Share", 4))
  # colnames(df) <- c("Value", "Organization", "Type")

# test <- as.data.frame(matrix(runif(10), 8, 1))
# 
# test[,2] <- c("Amnesty International", "Green Peace", "Oxfam", "Red Cross")
# test[,3] <- c(rep("Utility", 4), rep("Market Share", 4))
# colnames(test) <- c("Value", "Organization", "Type")
# 
# colors <- c("#ffc30b", "#3fad48", "#006633", "#660000")
# 
#   ggplotly(
#     ggplot(test, aes(y = Value, x = Organization, fill = Organization)) +
#            geom_col() +
#            labs(x="") +
#            scale_fill_manual(values = colors) +
#            theme(legend.position = "none") +
#            facet_wrap(~Type)
#   )
# })

@@

  ggplotly(ggplot(df, aes(y = Value, x = Organization, fill = Organization)) +
             geom_col() +
             labs(x="") + 
             scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
             theme(legend.position = "none") +
             facet_wrap(~Type)
    )
})
```
